Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Spellcheck and minor edits

---
title: "Country-Level Impact of Education on Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "10 december 2014"
linestretch: 2 
output: pdf_document
---

* * *

@@

*Introduction to Collaborative Social Science Data Analysis*

(The impact of self confidence on entrepreneurship.)

@@

### Why we chose to look into Education to explain Entrepreneurship - What has been done

Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or number of students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments. Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are. We see this process as manyfold but will only focus here on one of the potential causal relations. We want to understand specifically to want extent the support of individual self-confidence within education systems can affect the likelihood to become an entrepreneur, and thus impact the rate of entrepreneurship at the country level.

In trying to explore what supports entrepreneurship at the country-level, one should start by refering to what research asserted for that matter. For this purpose, we refer here to the OECD reports available online here http://www.oecd.org/std/business-stats/48129925.pdf. Two main sorts of determinants or favourable conditions have been looked into, that is environmental factors and individual factors. Although we intend to focus more on individual factors, we
want to mention here the environmental factors as they should be controled for. They actually divide into six broad categories:

**The regulatory framework**, which includes administrative burdens, regulations and frameworks, as well as fiscal policy parameters.

**The market conditions**, which include anti-trust laws, rules for competition, access to foreign markets, degree of public involvement and level of private demand.

**The access to finance**, which includes access to debt financing, access to venture capital, and stock markets.

**The creation and diffusion of knowledge**, which include research and development activity, transfer of non-commercial knowledge, co-operation among firms, technology availability and take-up.

**The entrepreneurial capabilities**, which includes business and entrepreneurship education as well as immigration.

@@

Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of self-confidence and entrepreneurial self-efficacy between countries. By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur. Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business. Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.

@@

Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.

@@

Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship. As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ??????? Boyd and Vosikis MAIN BIB ??????????? . One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in lign with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.

@@

The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controled for. To do so, we will look at the average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.

@@

The lack of suitable data as well as the fact that OECD PISA (Programme for International Student Assessment) tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being. But we still think that should be included in a future research on that topic.

@@

As we attempt to measure the impact of education systems' support of students' self-confidence on the rate of entrepreneurship at the country-level, we expect to observe different effects depending if we consider entrepreneurial intentions only or we also look into actual entrepreneurial activities. Even in measuring the impact on activities, we could potentially observe different effects between nascent and established entrepreneurship. Therefore, we will consider the three measures of entrepreneursip separately:

@@

To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).

@@

The NES is structured around nine entrepreneurial framework contitions evaluated by thirty-six experts in each surveyed country.  These nine entrepreneurial framework conditions are included below (a minimum of four experts must be interviewed on each of the framework conditions).

@@

The APS is a questionnaire distrubuted to a minimum of 2,000 adults in each participating country.  The survey is created by a central GEM team, but the implementation is managed by national teams that compete for the role of implementing the survey.  Experts are chosen based on experience and specialization and are expected to represent the entire country (including urban and rural areas).

@@

The process of importing, cleaning, and analyzing all of the data used in this project is fully documented and reproducable by referencing our GitHub repository.

@@

To understand the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship we built our model as outlined in the table below.

@@

Data on our explanatory variable, Way of Teaching, is available on the GEM website for the years 2001-2010.  To illustrate the distribution of this data, we have created the following histogram.  As shown in the histogram, the largest density of scores is approximately 2.3, which lies between the "somewhat false" and "neither true or false" categories.  This is not a whole number because the scores given by each of the 4 experts surveyed for each frameork condition are averaged to create a national-level number.  As discussed later in this paper, this presents some difficulties in drawing substantive conclusions from this data.  Namely, a large number of indifferent responses complicate the process of determining the influence we would like to analyze.

@@

# Library ggplot2
library("ggplot2")

# Create a histogram showing the distribution of Way of Teaching
qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .10)

@@

Starting with this explanatory variable, as mentioned earlier, we expected to observe different effects depending on the kind of entrepreneurship we looked at:

@@

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.  This relationship can be seen in the following regression output table.  This regression output was generated using a simple least square regression model.

@@

############ Running a regression with full df (including omitted variables)
RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
```

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

@@

To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.  Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.  A regression output table with these results has been included below.

# Run three regression equations again (omitting country-specific effects)
RG4 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG5 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG6 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

<br>
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.   Given the prevelence of omitted data in our data frame, we decided to attempt to increase the accuracy of this model by using the R program Amelia to generate an imputed data frame.  This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).  Equation  titled "Imputed" were calculated using this imputed data frame.

To generate the simulations, we decided to use the R package Zelig.  This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).  We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.  A regression output table and our simulation results are included below.  Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables."

@@

# Regression output table with country-specific effects
stargazer::stargazer(Z1, Z2,
                     title = 'Linear Regression Estimates omitting Country-specific Effects',
                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
                     font.size =  "small", type = 'latex', no.space = TRUE,
                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
```

@@

>>>>

---
title: "Country-Level Impact of Education on Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "10 December 2014"
linestretch: 2 
output: pdf_document
---

@@

@@

### Why we Chose to Look into Education to Explain Entrepreneurship - What Has Been Done

Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or number of students per class, we suggest to use another kind of indicator in order to trace the potential long-term investment made by governments. Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are. We see this process as many-fold but will only focus here on one of the potential causal relations. We want to understand specifically to want extent the support of individual self-confidence within education systems can affect the likelihood to become an entrepreneur, and thus impact the rate of entrepreneurship at the country level.

In trying to explore what supports entrepreneurship at the country-level, one should start by referring to what research asserted for that matter. For this purpose, we refer here to the Organisation for Economic Co-Operation and Development (OECD) list of indicator for entrepreneurial determinants available [here](http://www.oecd.org/std/business-stats/48129925.pdf). Two main sorts of determinants or favourable conditions, environmental factors and individual factors, have been identified and researched. Although we intend to focus more on individual factors, we want to mention here the environmental factors as they should be controlled for in our analysis. They have been divided into six broad categories by the OECD:

**The regulatory framework**: Including administrative burdens, regulations and frameworks, as well as fiscal policy parameters.

**The market conditions**: Including anti-trust laws, rules for competition, access to foreign markets, the degree of public involvement and level of private demand.

**The access to finance**: Including access to debt financing, access to venture capital, and stock markets.

**The creation and diffusion of knowledge**: Including research and development activity, the transfer of non-commercial knowledge, co-operation among firms, technology availability, and take-up.

**The entrepreneurial capabilities**: Including business and entrepreneurship education as well as immigration.

@@

Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of self-confidence and entrepreneurial self-efficacy between countries. By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur. Here, the variable "perceived capabilities" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business. Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.

@@

Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activated in France, and only on an voluntary individual teacher's basis.

@@

Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship. As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ??????? Boyd and Vosikis MAIN BIB ??????????? . One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in line with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.

@@

The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controlled for. To do so, we will look at the average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.

@@

The lack of suitable data as well as the fact that OECD PISA (Programme for International Student Assessment) tends to focus on different aspects of education systems for every triennial survey, lead us to give up on this for the time being. But we still think that should be included in a future research on that topic.

@@

As we attempt to measure the impact of education systems' support of students' self-confidence on the rate of entrepreneurship at the country-level, we expect to observe different effects depending if we consider entrepreneurial intentions only or we also look into actual entrepreneurial activities. Even in measuring the impact on activities, we could potentially observe different effects between nascent and established entrepreneurship. Therefore, we will consider the three measures of entrepreneurship separately:

@@

To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creativity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).

@@

The NES is structured around nine entrepreneurial framework conditions evaluated by thirty-six experts in each surveyed country.  These nine entrepreneurial framework conditions are included below (a minimum of four experts must be interviewed on each of the framework conditions).

@@

The APS is a questionnaire distributed to a minimum of 2,000 adults in each participating country.  The survey is created by a central GEM team, but the implementation is managed by national teams that compete for the role of implementing the survey.  Experts are chosen based on experience and specialization and are expected to represent the entire country (including urban and rural areas).

@@

Additional information on the GEM data used for this research can be seen in the descriptive statistics table included below.

```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis', warning=FALSE}

CD1 <- CD

# Remove uncessesary column
CD1$X <- NULL

# Set Year as factor
CD1[,"Year"] <- as.factor(CD1[,"Year"])

# Rename column
names(CD) <- gsub("PercentPerceived", "PerceivedCapability", names(CD))
names(CD1) <- gsub("PercentPerceived", "PerceivedCapability", names(CD1))

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}

# Generate descriptive statistics table
stargazer(CD1, type = "latex")
```
\end{singlespace}

@@

To understand the impact of educational factors -- specifically the encouragement of creativity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship we built our model as outlined in the table below.

@@

Data on our explanatory variable, Way of Teaching, is available on the GEM website for the years 2001-2010.  To illustrate the distribution of this data, we have created the following histogram.  As shown in the histogram, the largest density of scores is approximately 2.3, which lies between the "somewhat false" and "neither true or false" categories.  This is not a whole number because the scores given by each of the 4 experts surveyed for each framework condition are averaged to create a national-level number.  As discussed later in this paper, this presents some difficulties in drawing substantive conclusions from this data.  Namely, a large number of indifferent responses complicate the process of determining the influence we would like to analyze.

@@

# Create a histogram showing the distribution of Way of Teaching
Q <- qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .05)

Q + theme_bw()
```

In addition to understanding the density of each recorded "Way of Teaching" indicator, it is also helpful to examine the differences in this indicator among OECD countries.  To see this, we have created a figure showing the distribution of the average "Way of Teaching" value over the 2001-2010 period for the OECD countries included in the surveys.  This figure is included below.

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

# Drop unnecessary column 1
WayofTeaching$X <- NULL

# Change data from long to wide format
WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")

# Delete variable name in Year columns
names(WT) <- gsub("WayofTeaching.", "", names(WT))

# Duplicate df for future use
WT2 <- WT

# Generate a new column with mean of all other columns
WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010")), na.rm = TRUE)

# Drop year columns, leaving only mean column
WT$'2001' <- NULL
WT$'2002' <- NULL
WT$'2003' <- NULL
WT$'2004' <- NULL
WT$'2005' <- NULL
WT$'2006' <- NULL
WT$'2007' <- NULL
WT$'2008' <- NULL
WT$'2009' <- NULL
WT$'2010' <- NULL
WT$'2011' <- NULL
WT$'2012' <- NULL
WT$'2013' <- NULL
WT$row.names <- NULL

# Create 
WT[, 3] <- round(log(WT[, 3]), digits = 2)
```

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
library(googleVis)

# Plot
WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

@@

image: ![Way of Teaching](https://raw.githubusercontent.com/SamDund/Assign2Education/master/PresentationandPaper/images/WoTmap.png)

Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).  These three regression equations are as follows:

@@

-------------------------

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreneur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.  This relationship can be seen in table 4 below.  This regression output was generated using a simple least square regression model.

@@

############ Running a regression with full df (including omitted variables)
RG1 <- lm(PercentIntention ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG2 <- lm(PercentNascent ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG3 <- lm(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
```

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

```
\end{singlespace}

To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.  Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.  The results can be seen in table 5 below.

# Run three regression equations again (omitting country-specific effects)
RG4 <- lm(PercentIntention ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG5 <- lm(PercentNascent ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG6 <- lm(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

@@

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

```
\end{singlespace}

Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.   In an effort to address data availability issues, we also decided to run a second model including imputed data generated by the R program Amelia to generate an imputed data frame.  This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).  Equation  titled "Imputed" were calculated using this imputed data frame.

To generate the simulations, we decided to use the R package Zelig.  This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).  We chose to simulate values in our explanatory variable "Way of Teaching" and "Perceived Capabilities" for this analysis.  One important aspect of the Zelig package is that observations with omitted variables will be omitted from the calculation.  For this reason, there is some variation between the coefficients for the Zelig model and the model in the preceding regression output chart.

Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables." A regression output table and our simulation results are included below.

@@

# Regression output table with country-specific effects
stargazer::stargazer(Z1, Z2,
                     title = 'Least Squares Regression for Continuous Dependent Variables',
                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
                     font.size =  "small", type = 'latex', no.space = TRUE,
                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
```
\end{singlespace}

@@

As we can see from the regression output table, using the Amelia program to generate additional data expanded the observations analyzed from 172 to 318, and increased the statistical significance of our explanatory variable.  In addition, the positive slope of this equation is consistent with what we expected after our analysis of existing literature on this topic.  In addition, this process reduced the variance in our simulation results, suggesting it improved the accuracy of this model.  Despite this, we have several concerns regarding the reliability of existing GEM data (which will be discussed later in this paper), which makes us question the effectiveness of using this data to generate additional observations.

Perceived opportunities

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Library required packages
library(googleVis)
library(countrycode)
library(repmis)
library("ggplot2")
library("reshape2")

# Import GEM data frame
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PerceivedOpportunities$new.col <- D2

# Reorder columns so country code is first
D3 <- PerceivedOpportunities[,c(15,1:14)]

# Rename first column
D4 <- plyr::rename(x = D3, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(D4) <- gsub("X", "", names(D4))

# Set columns as numeric
D4[,"2001"] <- as.numeric(D4[,"2001"])
D4[,"2002"] <- as.numeric(D4[,"2002"])
D4[,"2003"] <- as.numeric(D4[,"2003"])
D4[,"2004"] <- as.numeric(D4[,"2004"])
D4[,"2005"] <- as.numeric(D4[,"2005"])
D4[,"2006"] <- as.numeric(D4[,"2006"])
D4[,"2007"] <- as.numeric(D4[,"2007"])
D4[,"2008"] <- as.numeric(D4[,"2008"])
D4[,"2009"] <- as.numeric(D4[,"2009"])
D4[,"2010"] <- as.numeric(D4[,"2010"])
D4[,"2011"] <- as.numeric(D4[,"2011"])
D4[,"2012"] <- as.numeric(D4[,"2012"])
D4[,"2013"] <- as.numeric(D4[,"2013"])

# Create country vector to subset
myvars2 <- c('US','FR','DE','JP','GB')

# Subset Opp2
Opp2 <- subset(D4, iso2c %in% myvars2)

# Melt Opp2 df
Opp3 <- melt(data = Opp2,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Edit column names
names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
names(Opp3) <- gsub("variable", "Year", names(Opp3))

Opp3$iso2c <- NULL
```

```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

# Create plot
G1 <- ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()

G1 + ggtitle("Perceived Opportunities Over Time") + theme_bw()
```
